Gamification Effectiveness on Education

### 2024-04-09 paper/paper.qmd
added references to the paper I am using and other common libraries I am been using

library(tidyverse)
library(palmerpenguins)
```

@@

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

>>>>

library(tidyverse)
library(palmerpenguins)
library(arrow)
```

@@

analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
